Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-14 writeup/gz_hubble_data.tex
updating threshold values in writeup

\begin{table*}
\caption{Cookbook \label{tab:prev_tasks}}
\begin{tabular}{llll}
\hline\hline
Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
         &            	        &                & $N_{task} \ge 20$ \\
\hline
01       & smooth or features   &  -                  & -                 \\
02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.3$              \\
03       & bar		        & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                  \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.85$         \\
06       & odd yes/no           & -                   &                   \\
07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
13       & bright clump         & 01, 12, 16          & $p_{\rm one~clump}<$                 \\
14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright~clump,yes}>$           \\
15       & clump arrangement    & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
18       & clumps embedded      & 01, 12, 16          &  $p_{\rm multiple~clumps}>0.45$                 \\

>>>>

\begin{table*}
\caption{Cookbook \label{tab:prev_tasks}}
\begin{tabular}{llll}
\hline\hline
Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
         &            	        &                & $N_{task} \ge 20$ \\
\hline
01       & smooth or features   &  -                  & -                 \\
02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.3$              \\
03       & bar		        & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.65$         \\
04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                  \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.65$         \\
05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>0.25$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>0.65$         \\
06       & odd yes/no           & -                   &                   \\
07       & rounded              & 01                  & $p_{\rm smooth}>0.7$               \\
08       & odd feature          & 06                  & $p_{\rm odd,yes}> 0.5 $                  \\
09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>0.4$               \\
10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$ 0.25                 \\
11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$ 0.25                \\
12       & clumpy               & 01                  & $p_{\rm features}>0.23$              \\
13       & bright clump         & 01, 12, 16          & $p_{\rm one~clump}< 0.4$                 \\
14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright~clump,yes}>0.5$           \\
15       & clump arrangement    & 01, 12, 16          & $p_{\rm multiple~clumps}>0.45$                \\
16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.8$              \\
17       & clumps symmetrical   & 01, 12              & $p_{\rm clumpy,yes}>0.8$                \\
18       & clumps embedded      & 01, 12              & $p_{\rm clumpy,yes}>0.8$                 \\
